Title

### 2024-02-09 index.qmd
freeze headers of table

<div class="table-wrapper">
```{r sample-population-characteristics}
cc2000_edition_data <- read_excel(file.path(data_dir, 'cc2000_edition_data.xls'), sheet = 'Data')
pop_pubu <- (cc2000_edition_data %>% filter(`Control (text)` == 'Public', `CC2000 (text)` == 'Doctoral/Research Universities—Extensive'))$UNITID %>% as.character()

>>>>

<div class="table-wrapper freeze-col">
```{r sample-population-characteristics}
cc2000_edition_data <- read_excel(file.path(data_dir, 'cc2000_edition_data.xls'), sheet = 'Data')
pop_pubu <- (cc2000_edition_data %>% filter(`Control (text)` == 'Public', `CC2000 (text)` == 'Doctoral/Research Universities—Extensive'))$UNITID %>% as.character()
